A possibilistic valid-time model

### 2011-11-15 ipmu2012/proposal.tex

\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.2]{graphs/2_triangular.eps}
  \caption{Two fuzzy numbers $X$ and $Y$ denoting a Possibilistic Valid-Time Period \emph{PVT}.}
  \label{fig:pvp}
\end{figure}

@@

\subsection{Querying ill-known valid-time intervals}

\subsubsection{Query specification}

\subsubsection{Query evaluation}

>>>>

\begin{figure}[h!]
  \centering
%  \includegraphics[scale=0.2]{graphs/2_triangular.eps}
  \caption{Two fuzzy numbers $X$ and $Y$ denoting a Possibilistic Valid-Time Period \emph{PVT}.}
  \label{fig:pvp}
\end{figure}

@@

\subsection{Querying ill-known valid-time intervals}
In order to provide a complete model, we will provide the tools for querying. This allows the user to specify both the preferences and an ill-known valid-time interval in the query. It is important to notice that the possibilistic / fuzzy data stored in the database has a \emph{disjunctive interpretation} (it is said that we have \emph{uncertainty}: the valid-time interval has only one value but, for some reason the value is ill-known). In the query specification, the user is allowed to express \emph{imprecision} or \emph{vagueness} (this is referred as a \emph{conjunctive interpretation}).
In this subsection we will define the query specification, then the evaluation of the query and finally the ranking for the query.

\subsubsection{Query specification}
A query in our framework has two different parts: the first one is the query specification for regular attributes. The second part is the temporal specification.

\begin{definition}
A query $\tilde Q$ is specified by:
\begin{equation}
\tilde Q = \left( Q^{time}, Q \right)
\end{equation}
\end{definition}
Where $Q$ are the (possibly fuzzy) preferences of the user  and $Q^{time}$ is the temporal part specified by a possibilistic valid-time period,\emph{PVP}.

%explain the sematics of vt.

\subsubsection{Query evaluation}
Fuzzy querying of regular (relational) databases, query satisfaction modelling is a matter of degree. Usually, criteria satisfaction is modelled by means of a satisfaction degree $s \in \left[ 0, 1\right]$. In the model, every record $r$ contains a \emph{PVP} $V_r$ to model the valid-time for that record.

The query evaluation method is the following:
\begin{itemize}
\item
For each record $r$ in the database, the preferences expressed in $Q$ are evaluated in the unit interval.
\end{itemize}
